% ========== English resume content: edit this file only ==========
% Replace all placeholder text with your own information.

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Your Name} & Email : \href{mailto:your.email@example.com}{your.email@example.com}\\
  Your Job Title & Phone : (123) 456-7890 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Example University}{City, Country}
      {M.S. / B.S. in Your Major; GPA: X.X/4.0}{Sep. 20XX -- June 20XX}
    \resumeSubheading
      {Another University}{City, Country}
      {B.S. in Related Field; Honors if any}{Sep. 20XX -- June 20XX}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Company Name A}{City, Country}
      {Your Role Title}{Month 20XX - Present}
      \resumeItemListStart
        \item \textbf{Project or responsibility name}:
          \begin{itemize}[parsep=0pt, itemsep=1pt, leftmargin=*]
            \item First point: description and impact; use metrics where possible (e.g., improved X by Y\%, reduced latency to Z).
            \item Second point: another outcome or responsibility.
            \item Third point: add more \verb|\item| as needed.
          \end{itemize}
        \resumeItem{Another responsibility}
          {Single-line description when you do not need sub-bullets.}
      \resumeItemListEnd

    \resumeSubheading
      {Company Name B}{City, Country}
      {Previous Role}{Month 20XX - Month 20XX}
      \resumeItemListStart
        \resumeItem{Key project or initiative}
          {Brief description and outcomes.}
        \resumeItem{Another responsibility}
          {Another bullet with results.}
      \resumeItemListEnd

    \resumeSubheading
      {Company Name C (Intern)}{City, Country}
      {Intern Role}{Month 20XX - Month 20XX}
      \resumeItemListStart
        \resumeItem{Internship focus}
          {What you built or contributed.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%--------TECHNICAL SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
    \item{
     \textbf{Category 1}{: Skill A, Skill B, Skill C; tools or frameworks.}
     \vspace{-4pt}
    }
    \item{
     \textbf{Category 2}{: Relevant technologies and experience.}
     \vspace{-4pt}
    }
    \item{
     \textbf{Category 3}{: Languages, platforms, or other.}
     \vspace{-4pt}
    }
    \item{
     \textbf{Tools \& Other}{: Development tools, version control, OS, etc.}
    }
 \resumeSubHeadingListEnd
